What is an Ancestral Recombination Graph?

### 2022-02-28 paper.tex

\end{tikzpicture}
\caption{\label{fig-arg-data-structure}
Node vs edge breakpoint annotations.
The classical approach described by Griffiths
equates graph nodes with events in the stochastic process,
and associates recombination breakpoint information with \emph{nodes} (left).
This encoding
is limited in the pattern of inheritance that can be described
and requires that edges be ordered to avoid ambiguity.
[TODO clarify that the function is the same things as having two
types of nodes]
The alternative is to associate breakpoint annotations
with \emph{edges} (right).
Associating the interval of genome inherited by the child node
from the parent with the corresponding edge, allows
any pattern genetic inheritance to be described and does
not required edges to be ordered.
}
\end{figure}

>>>>

\end{tikzpicture}
\caption{\label{fig-arg-data-structure}
Node vs edge breakpoint annotations.
The classical approach described by Griffiths
equates graph nodes with events in the stochastic process,
and associates recombination breakpoint information with \emph{nodes} (left).
This encoding
is limited in the patterns of inheritance that can be described
and requires that edges be ordered to avoid ambiguity.
[TODO clarify that the function is the same things as having two
types of nodes]
The alternative is to associate breakpoint annotations
with \emph{edges} (right).
Associating the interval of genome inherited by the child node
from the parent with the corresponding edge allows
any pattern genetic inheritance to be described and does
not require edges to be ordered.
}
\end{figure}
